\documentclass[11pt,a4paper]{article}
\usepackage[inline]{enumitem}
\setlist[itemize]{topsep=6pt}
\usepackage{titlesec}
\titleformat{\subsection}[block]{\Large\bfseries\filcenter}{}{1em}{}
\usepackage[nohead,nofoot,hmargin=2cm,vmargin=1cm]{geometry}
\usepackage{tabularx}
\usepackage{xtab}
\usepackage{wasysym}
\usepackage{marvosym}
\usepackage{hyperref}
\usepackage{mathptmx}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{etoolbox}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
  }
  
\makeatletter
\preto{\@tabular}{\parskip=0pt}
\makeatother
\addtolength{\parskip}{-0.5mm}
\setlength\parindent{0pt}
%course/job title ; employer/institution ; dates
\newcommand{\centry}[3]{\paragraph{#1} \textit{#2}%
\hfill#3\\[2pt]}
%
\renewcommand{\familydefault}{\sfdefault}


\begin{document}
\begin{tabularx}{\linewidth}{XX}
  \begin{flushleft}
    {\large LARA RUDIN}\\[\baselineskip]
  \end{flushleft}
&
  \begin{flushright}
    \href{tel:+447759302861}{+44 7759 302861}\\
    \href{mailto:lara@rudin.co.uk}{lara@rudin.co.uk}\\[\baselineskip]
    2 Sedley Taylor Road,\\
    Cambridge, CB2 8PW
  \end{flushright}
\end{tabularx}

\rule{\textwidth}{1pt}

\subsection*{Summary}

I am a motivated and organised individual; I have just finished studying at the
University of Liverpool. Due to my extensive hospitality experience, I excel
working under pressure and I am a good multitasker. I always maintain a
positive attitude and believe I can bring energy and charisma into my work
life. I work well both in a team and on my own as I am independent and a
self-starter.

\subsection*{Education}

\centry{GCSEs}{The Netherhall School, Cambridge}{2009--2014}
\begin{center}
  \begin{tabular}{llll}
    Maths & B & Physics & A \\
    Biology& A & Chemistry& A \\
    English Literature& B & English Language& B \\
    PE& A* &  History& A\\
    French& B & Art& A\\
  \end{tabular}
\end{center}

\centry{A levels}{Hills Road Sixth Form College}{2014--2016}
\begin{center}
  \begin{tabular}{llll}
    Psychology & A* & Biology & C \\
    Philosophy & B  & Classical Civilisation (AS Level) & C\\
  \end{tabular}
\end{center}
\centry{Psychology BSc (Hons) 2:1}{University of Liverpool}{2017--2020}

I chose to study psychology due to my avid interest at A-level which carried
through to my degree. I thoroughly enjoyed my degree as I was able to study
aspects of psychology that I have always found most fascinating, such as social
psychology and body image research.

\begin{tabularx}{\linewidth}{XX}
  \begin{flushleft}
    \begin{tabular}{ll}
      First year overall grade: & 74.2\% & Second year overall grade: & 67.3\% \\
      \\
      \textbf{Second year modules} & \textbf{Grade (\%)}\\
      Clinical and Forensic Psychology & 65\\
      Psychobiology and Motivation & 63\\
      Methods and Statistics 1& 69\\
      Lifespan and Development &69\\
      Mind and Brain& 68\\
      Methods and Statistics 2&72\\
    \end{tabular}
  \end{flushleft}
  &
  \begin{flushright}
    \begin{tabular}{ll}
      \\
      Third year overall grade: 67.6\% \\
      \\
      \textbf{Third year modules} & \textbf{Grade (\%)}\\
      Appetite Regulation and Obesity &67\\
      Media Psychology & 69\\
      Psychological Issues in Adult Ageing& 61\\
      Research Project & 69\\
      Applied Social Psychology & 69\\
      Brain and Behaviour & 71\\
      Psychology of Health & 66\\
    \end{tabular}
  \end{flushright}    
\end{tabularx}

\subsection*{Experience}

\centry{Research Internship}{Liverpool University}{Oct 2019--present}

I worked alongside Dr Paul Christiansen and Dr Andrew Jones performing
statistical surveying and analysis of information required for a study on field
of addiction. We expect to publish in an academic journal. I gained knowledge
of the academic publication process for psychologists; I also gained skills of
carrying out professional research and analysis of data to the highest
standard.

\centry{Student Brand Ambassador}{Seed Marketing}{Sept 2019--Dec 2019}

I was responsible for encouraging students within my university to visit
Revolution bars by promoting Revolutions at student fairs, engaging with
students on campus and posting on various social media platforms.  I gained
skills in specific student marketing tactics on social media to effectively
appeal to students. I was awarded a prize for the best social media post across
all UK Student Brand Ambassadors.

\centry{Waiting staff}{Wimbledon Championships}{July 2019}

I worked in a highly professional environment providing the best level of
service and conduct for a prestigious event. I worked with a high volume of
customers, completing tasks quickly and to a high standard.

\centry{Waitress}{Leaf restaurant}{Mar 2019--May 2019}

Experience included: waiting on tables for breakfast, lunch and evening
service, bar work such as serving drinks, restocking fridges and stock
handling. Cleaning and using the barista coffee machine, cash handling, till
service and expert menu knowledge.

\centry{Shift supervisor}{The Little Cupcake Company}{Sept 2016--Feb 2017}

I gained experience in opening and closing duties, hygiene auditing, stock
intake, cash handling, basic food preparation and training new staff. I was
constantly involved in direct sales at this outlet in a busy shopping centre.

\centry{Waiting Staff}{Downing College, Cambridge University}{Nov
  2015--present}

Experience includes: silver service for busy events and dinners; standing and
seated waiting; daytime and evening service; and serving and preparing
weddings.


\subsection*{Skills}
\begin{itemize}[noitemsep]
  \item First Aid Certificate
  \item Sports Leadership Certificate 
  \item Microsoft Office Intermediate skills
  \item University of Liverpool Athletics and Cross-Country Society Treasurer
  \item Clean driving licence 
  \item I have both British and Irish nationality 
\end{itemize}
\subsection*{Interests}
\begin{itemize}[noitemsep]
  \item Running half marathons
  \item Travelling: during my gap year before university I travelled around
    South East Asia for four months. During my time travelling I learnt lots
    about the rich and vibrant cultures, this fascinated me and fuelled my
    interest for travelling and experiencing new places. 
  \item Attending social and music events
  \item Cooking and baking 
\end{itemize}

\subsection*{References}

\begin{tabularx}{\linewidth}{XX}
  \begin{flushleft}
    Carine Van Der Boor\\
    University tutor\\
    \href{mailto:c.van-der-boor@liverpool.ac.uk}{c.van-der-boor@liverpool.ac.uk}\\
    \href{tel:+441517946705}{+44 1517 946705}\\
  \end{flushleft}
  &
  \begin{flushright}
    Joan Belgrove\\
    Manager: The Little Cupcake Company Manager\\
    \href{mailto:office@thelittlecupcakecompany.co.uk}{office@thelittlecupcakecompany.co.uk}\\
    \href{tel:+447979750649}{+44 7979 750649}\\


  \end{flushright}
\end{tabularx}


\end{document}
